### 2022-05-31 article.tex
Use correct picture

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{DNA_to_protein_or_ncRNA.png}
  \caption{
    Parts of DNA (so-called 'genes') code for proteins. 
    The DNA, that always stays put in the cell's nucleus, 
    is transcripted to messenger RNA (mRNA).
    mRNA leaves the nucleus and its code gets translated to 
    a protein sequence.
    Near the start of a gene are regions that determine the amount
    of proteins produced (not shown in figure).
    Adapted from \cite{shafee2015}
  }
  \label{fig:dna_to_protein}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{baggerly2009deriving_fig_1a_zoom.png}
  \includegraphics[width=\linewidth]{baggerly2009deriving_fig_1a.png}
  \caption{
    A published off-by-one error.
    Left: a zoom in. 
    Horizontal axis is the sample name.
    Vertical axis is UNKNOWN.
    Color in the cell denotes gene expression.
    The colors above the cells, with the dendrogram, shows
    red for non-responders (red) and responsive (blue).
    Right: visisualization of sample that shows samples are duplicated,
    as annotated by the pink rectangles. Note that, due to this, some
    samples are both non-responders and responders.
    Adapted from \cite{baggerly2009deriving}
  }
  \label{fig:baggerly2009deriving}
\end{figure}

>>>>

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{DNA_to_protein.png}
  \caption{
    Parts of DNA (so-called 'genes') code for proteins. 
    The DNA, that always stays put in the cell's nucleus, 
    is transcripted to messenger RNA (mRNA).
    mRNA leaves the nucleus and its code gets translated to 
    a protein sequence.
    Near the start of a gene are regions that determine the amount
    of proteins produced (not shown in figure).
    Adapted from \cite{shafee2015}
  }
  \label{fig:dna_to_protein}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{baggerly2009deriving_fig_1a.png}
  \caption{
    Gene expression result due to an off-by-one error.
    The cells in the main table show how much mRNA is produced per cell 
    line (the columns) for different proteins (the rows).
    The colors above the cells, with the dendrogram, shows
    red for cells that do not respond (red) and do respond (blue) to an 
    antibiotic.
    The purple rectangles show samples that are duplicated.
    Note that, due to this, some
    samples that behave identically are both non-responders and responders.
    From \cite{baggerly2009deriving}
  }
  \label{fig:baggerly2009deriving}
\end{figure}
